---
output: 
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    number_sections: yes
geometry: margin=2.54cm
title: "Is big tech greenwashing?"
subtitle: "https://github.com/amandafbooth/BoothProphete_ENV872_EDA_FinalProject"
author: "Amanda Booth and Ricky Prophete"
fontsize: 12pt
mainfont: Times New Roman

---

\newpage
\tableofcontents 
\newpage
\listoftables 
\newpage
\listoffigures 
\newpage

```{r setup, include=FALSE}
# Set your working directory

# Load your packages

library(tidyverse)
library(corrplot)
library(knitr)

#Build theme
mytheme <- theme_linedraw(base_size = 10) +
  theme(axis.text = element_text(color = "rosybrown"), 
        legend.position = "bottom")

#Set as default theme
theme_set(mytheme)

#Load data

company_selection_clean <- read.csv("./Data/Processed/Company_Selection_Clean.csv")

Reporting_inconsistencies_processed <- read.csv("./Data/Processed/Reporting_inconsistencies_processed.csv")

Energy_Usage_Clean <- read.csv("./Data/Processed/Energy_Usage_Clean.csv")

#Join datasets 

company_profiles <- left_join(company_selection_clean, Reporting_inconsistencies_processed)

company_profiles <- left_join(company_profiles, Energy_Usage_Clean)

#Filter out 1.0 ratios 

company_profiles2 <- company_profiles[!is.na(company_profiles$Company.report),]
  

```


# Rationale and Research Questions



\newpage

# Dataset Information

## Data Retrieval 

For this analysis, we used data analyzed in a *Nature Communications* study that took data from 2019 CDP reports. CDP, a carbon footprint registry for companies and municipalities, conducts an in-depth questionnaire that inquires about the details of what entities do and don’t include in their carbon emissions reporting. The *Nature* study compared what technology companies published in their official company reports to what companies reported in CDP questionnaires and found technology companies often under reported emissions in official company reports. The data from nature came in the form of an Excel Workbook with many panels. We converted three panels into CSVs for analysis in R:

* Company information 
* Emissions predictors
* Reporting inconsistencies 

Table 1: Data Information

**Detail**           | **Description**
---------------------| -------------
Data Source          | Nature Communications
Retrieved from       | https://www.nature.com/articles/s41467-021-26349-x
Variables Used       | Company, Sales, Profits, Assets, Market value, Company report, 
CDP emissions, Emission reports deviation, Reporting inconsistency ratio, Total energy consumption 
Data Collection Year | 2019
\newpage

# Exploratory Analysis 


```{r top5, echo=FALSE}
top5 <- company_profiles2 %>% 
  slice_max(Inconsistency_ratio, n = 5) %>%
  select(Company, Inconsistency_ratio)

kable(top5, caption = "Top 5 Companies by Highest Reporting Inconsistency Ratio", align = 'l')
```


\newpage

# Analysis



## Question 1: <insert specific question here and add additional subsections for additional questions below, if needed>

## Question 2: 




\newpage

# Summary and Conclusions

We did not find a statistically significant relationship between companies’ reporting discrepancy ratios and variables that indicate size. As expected, we found a relationship between total energy consumption and size indicators. But surprisingly the indicator with the most confidence was value of assets. 

```{r plot1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Relationship between asset value and total energy consumption"}

options(scipen=5) 

Plot1 <- ggplot(company_profiles2, aes(x = Assets, y = Total.energy.consumption)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Value of assets (in millions)", y = "Total energy consumption (MWh)")
print(Plot1)

```

Our assumption that “big tech” would show more reporting discrepancies was not borne out in the data we analyzed. In future analyses on this topic, we would ideally have access to more CDP reports and more corporate reports in order to have a sample size that allows for more statistically accuracy. 

\newpage

# References

Klaaßen, Lena, and Christian Stoll. “Harmonizing Corporate Carbon Footprints.” Nature News, Nature Publishing Group, 22 Oct. 2021, https://www.nature.com/articles/s41467-021-26349-x. 